Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-11-10 Paper/ms.tex
Included H
Figure sizes

The marginal likelihood was $\ln(\mathcal{Z}) \approx -217.04$.

\begin{figure}
\includegraphics[scale=0.5]{Figures/nu_oph_N.eps}
\caption{The posterior distribution for the number of planets $N$ orbiting
$\nu$ Oph.\label{fig:nu_oph_N}}
\end{figure}

\begin{figure}
\includegraphics[scale=0.5]{Figures/nu_oph_periods.eps}
\caption{The posterior distribution for the orbital periods in the $\nu$ Oph
system.\label{fig:nu_oph_periods}}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{Figures/gliese581_N.eps}
\caption{The posterior distribution for the number of planets $N$ orbiting
Gliese 581.\label{fig:gliese581_N}}
\end{figure}

\begin{figure}
\includegraphics[scale=0.5]{Figures/gliese581_periods.eps}
\caption{The posterior distribution for the orbital periods in the Gliese 581
system.\label{fig:gliese581_periods}}
\end{figure}

The marginal likelihood was $\ln(\mathcal{Z}) \approx -618.04$.

>>>>

The marginal likelihood was $\ln(\mathcal{Z}) \approx -217.04$ and the
information was $\mathcal{H} \approx 80.0$ nats.

\begin{figure}
\includegraphics[scale=0.45]{Figures/nu_oph_N.eps}
\caption{The posterior distribution for the number of planets $N$ orbiting
$\nu$ Oph.\label{fig:nu_oph_N}}
\end{figure}

\begin{figure}
\includegraphics[scale=0.45]{Figures/nu_oph_periods.eps}
\caption{The posterior distribution for the orbital periods in the $\nu$ Oph
system.\label{fig:nu_oph_periods}}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.45]{Figures/gliese581_N.eps}
\caption{The posterior distribution for the number of planets $N$ orbiting
Gliese 581.\label{fig:gliese581_N}}
\end{figure}

\begin{figure}
\includegraphics[scale=0.45]{Figures/gliese581_periods.eps}
\caption{The posterior distribution for the orbital periods in the Gliese 581
system.\label{fig:gliese581_periods}}
\end{figure}

The marginal likelihood was $\ln(\mathcal{Z}) \approx -618.04$ and the
information was $\mathcal{H} \approx 140.2$ nats.
